\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-21 notes/notes.tex
replaced other figures with Ub=-U by 10

\paragraph{Important points regarding notation}
\begin{itemize}
	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0\). This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).	
\end{itemize}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
phase & RG flow & fixed point & GS & 2-site GS \\ 
\hline
blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
yellow &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
\hline
\end{tabular}
\end{center}

@@

\subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.050.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=5.000.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
\end{center}

\subsection*{Spin and charge correlations in ground state}
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.050.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=5.000.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=50.000.pdf}
\end{center}

@@

\subsection*{Perturbation theoretic terms}
These quantities are related to the local Fermi liquid of the Kondo strong-coupling fixed point and the perturbation theory associated with it. \(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations. \(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping. \(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}

\subsection*{Correlation within the Kondo cloud}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}

\subsection*{Mutual information between various real space members}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}

@@

\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}

@@

\subsection*{Real-space correlations}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}

	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}

>>>>

\paragraph{Important points regarding notation}
\begin{itemize}
	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\). This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).	
\end{itemize}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
phase & RG flow & fixed point & GS & 2-site GS \\ 
\hline
blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
gray &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
\hline
\end{tabular}
\end{center}

@@

\subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
\end{center}

\subsection*{Spin and charge correlations in ground state}
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=50.000.pdf}
\end{center}

@@

\subsection*{Perturbation theoretic terms}
These quantities are related to the local Fermi liquid of the Kondo strong-coupling fixed point and the perturbation theory associated with it. \(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations. \(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping. \(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

\subsection*{Correlation within the Kondo cloud}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

\subsection*{Mutual information between various real space members}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

@@

\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}

@@

\subsection*{Real-space correlations}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}

	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}
